%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Pursottam Sah resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% formatting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{article}
\usepackage[hmargin=0.75cm, vmargin=1cm]{geometry}

\usepackage[hidelinks]{hyperref}  % links (href)

\usepackage{multicol}     % 2 columns
\usepackage{titlesec}

\titleformat{\subsubsection}[runin]{
  \fontsize{10pt}{0pt}
  \bfseries
}{}{}{}[]

\titleformat{\section}{
  \fontspec[Path = fonts/ZillaSlab/]{ZillaSlab-Light}\fontsize{16pt}{24pt}\selectfont \raggedright\uppercase
}{}{0em}{}

% fonts
\usepackage[]{fontspec}
\setmainfont[Path = fonts/OpenSans/OpenSans/, BoldItalicFont=OpenSans-MediumItalic, BoldFont=OpenSans-Medium, ItalicFont=OpenSans-MediumItalic]{OpenSans-Light}

% Bullet Lists with fewer gaps command
\newenvironment{tightemize}{
\vspace{-\topsep}\begin{itemize}\itemsep1pt \parskip1pt \parsep0pt}
{\end{itemize}\vspace{-\topsep}}


% Section seperators 
\usepackage{titlesec}
\titlespacing{\section}{0pt}{0pt}{0pt} 
\titlespacing{\subsection}{0pt}{0pt}{0pt}
\newcommand{\sectionsep}{\vspace{8pt}}

% custom commands
\newcommand{\namesection}[3]{
  \begin{multicols}{2}
    \begin{flushleft}
      \fontsize{30pt}{25pt}
      \fontspec[Path = fonts/ZillaSlab/]{ZillaSlab-Light}
      {{ #1 } {#2 }}
      \columnbreak\\
    \end{flushleft}
    \begin{flushright}
      { #3 }
    \end{flushright}
  \end{multicols}
  \vspace{-10pt}
}

 
\newcommand{\subheading}[2]{
  {\subsubsection*{#1}
  \hfill #2} 
}
\newcommand{\upper}[1]{
  \MakeUppercase{#1}
}

\newcommand{\projname}[2]{
  {\large{#1}
  \hfill \small{#2}} 
}

\newcommand{\company}[2]{
  {\Large{{#1}}
  \hfill \footnotesize{#2}}
}

\newcommand{\role}[2]{
  {\large {{#1}}
    \hfill \small{#2}
  }
}

\newcommand{\loc}[2]{
  {\small{#1} 
  \hfill \small{#2}}
}

%%%%%%%%%%%%%%%%%%%%
% PERSONAL DETAILS
%%%%%%%%%%%%%%%%%%%%

\begin{document}

\namesection{Pursottam}{Sah}{
  +91 (603) 393-8402\\
  \href{mailto:rahulsah6003@gmail.com}{rahulsah6003@gmail.com}\par
  National Institute of Technology\\
  Arunachal Pradesh (IN)
}

\centering{
  LinkedIn:// \href{https://linkedin.com/in/pursottamsah}{\textbf{pursottamsah}} |
  \href{https://Pursottam6003.github.io/Portfolio}{purottam6003.github.io} |
  GitHub:// \href{https://github.com/Pursottam6003}{\textbf{Pursottam6003} }
}

\begin{multicols}{2}
  \begin{flushleft}
    \section*{Education}
    \subsection*{\href{http://nitap.ac.in/}{NIT Arunachal Pradesh}}
    \subheading{B. Tech in Computer Science Eng}{Oct 2020-2024} \\
    {Cum. GPA: \textbf{8.84 / 10 (Expected)}} 

    \subsection*{\href{https://roing.nic.in/public-utility/govt-hr-secondary-school-roing/}{Govt. Higher Sec. School, Roing}}
    \subheading{Higher Secondary, XII (CBSE)}{Grad. Aug 2020} \\
    {Cum. Percentage: \textbf{84.8}} 

    \subsection*{\href{https://roing.nic.in/public-utility/govt-hr-secondary-school-roing/}{Govt. Higher Sec. School, Roing}} 
    \subheading{Secondary, X (CBSE)}{Grad. April 2018} \\
    {Cum. Percentage: \textbf{89.4}} \\

    %%%%%%%%%%%%%%
    % Course Work
    %%%%%%%%%%%%%%
    \section*{Coursework}
    \begin{tightemize}
      \item  {Data Structures \& Algorithms} 
      \item  {Object Oriented Programming}
      \item  {Operating Systems} 
      \item  {Optimization Methods} 
      \item  {Machine Learning}
      \item  {Unix Tools and Scripting} \\
    \end{tightemize}

    %%%%%%%%%%%%%%
    % Experience 
    %%%%%%%%%%%%%%
    \section*{Experience}
    \company{\textbf{\href{https://iocl.com/}{Indian Oil Corp. Limited}}}{\textbf{Dec 2022 - Present}} \\
    \role{\textbf{Software Development Internship}}{Ghy, Assam (IN)}
    \begin{tightemize}
      \item {\textbf{Secured} the  \textbf{3\textsuperscript{rd}} rank in  college \textbf{internship selection test} and  \textbf{selected} for this \textbf{internship}}
      \item {Currently \textbf{working} on a lightweight \textbf{app development} project for the \textbf{company}} 
    \end{tightemize}


    \company{\textbf{\href{https://ekarigari.in/}{Ekarigari Systems Pvt. Ltd}}}{\textbf{July 2022 - Aug 2022}} \\
    \role{{\textbf{IoT and ML Trainee}}}{Remote }
    \begin{tightemize}
      \item  Acquire a basic understanding of \textbf{3} microcontroller
            boards, such as the \textbf{NodeMCU, Arduino UNO, and Raspberry
            Pi.}
      \item A \textbf{beta version} of the \textbf{Bus Tracking and Navigation
            System} was completed for more than \textbf{1000 college
            students.}
    \end{tightemize}

    \company{\textbf{\href{https://www.linkedin.com/company/rebert-tech/about/}{Rebert Technoliges Pvt. Ltd}}}{\textbf{June 2022 - July 2022}}
    \role{{\textbf{Software Development Internship}}}{Pune (Remote)}
    \begin{tightemize}
      \item  Worked on the current project of the company
            \textbf{‘DoBuizz’} where  \textbf{reduced} the team workload by \textbf{25}\%.
      \item \textbf{Update} and modify the 
      admin panel using \textbf{Javascript}
            functions and \textbf{fetch} the data from \textbf{Firebase Realtime
            Database.}
    \end{tightemize}

    \company{\textbf{\href{https://www.businesswebsolutions.in/}{Business Web Solutions Inc}}} {\textbf{May 2022 - July 2022}} \\
    \role{\textbf{Web Development Internship}}{Remote (IN)}
    \begin{tightemize}
      \item { Increase the \textbf{efficiency} of \textbf{Python} scripting by \textbf{70\%} with
      an understanding of \textbf{ HTML, CSS, and Javascript.}}
      \item {Utilizing \textbf{SQL} for the creation of \textbf{databases} as a
      backend which \textbf{improves} the faster \textbf{retrieval} by \textbf{20\%}} 
    \end{tightemize}

    %%%%%%%%%%%%%%
    % Skills 
    %%%%%%%%%%%%%%

    \section*{Skills} 
    \subsection*{Programming \\} 
    \begin{tightemize}
      \item \textbf{Languages:} C, C++, Java
      \item \textbf{Scripting:} Bash, Python
      \item \textbf{Frameworks:} React, Flask, Node
      \item \textbf{Database:} SQL, Firebase
      \item \textbf{Platforms:} Linux,Windows
      \item \textbf{Familiar:} Typescript
      \item \textbf{Others:} git, Microsoft Office
    \end{tightemize}

    \subsection*{Soft Skills}
    Leadership \textbullet{} Teamwork \textbullet{} Communication \textbullet{} Organization




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section*{Projects}
    \projname{\textbf{\upper{{Airavat tracker}}}}{\href{https://github.com/tripathics/airavat}{Source Code}} \\
    \loc{{\textbf{Nov 2022 - Present}}}{NIT Arunachal Pradesh (IN)}
    \begin{tightemize}
      \item  A \textbf{beta version} of the \textbf{Bus Tracking and Navigation.}
      System was completed for more than \textbf{1000 college
      students.}
      \item A \textbf{lightweight website} is developed and \textbf{Flask} is used as a framework. As hardware components, we used the \textbf{Node MCU (ESP8266)} and \textbf {GPS Module (NEOSIM900A)}.
    \end{tightemize}


    \projname{\textbf{\upper{{Technodaya Newsletter App}}}}{\href{https://technodaya.netlify.app/}{Source Code}} \\
    \loc{{\textbf{Sept 2022 - Present}}}{NIT Arunachal Pradesh, Itanagar (IN)}
    \begin{tightemize}
      \item   \textbf{The newsletter website of NIT Arunachal Pradesh.}
      \item   \textbf{Admin} can fill out the form and generate monthly.
      magazines which \textbf{reduce} our official \textbf{mail traffic by 17\%}.
      \item   \textbf{ReactJs} is used in frontEnd and \textbf{ Google Firebase} is used as a
      backend for \textbf{server authentication}, and \textbf{databases} of magazines.
    \end{tightemize}

    \projname{\textbf{\upper{{Ecommerce Webiste}}}}{\href{https://pursottam6003bakewithlove.netlify.app/}{Source Code}} \\
    \loc{{\textbf{Sept 2022 - Present}}}{NIT Arunachal Pradesh, Itanagar (IN)}
    \begin{tightemize}
      \item  Developed \textbf{E-Commerce} Web application \textbf{Bake with Love.}
      \item  \textbf{ReactJs} is used in the \textbf{frontend} and \textbf{Firebase} is used at
      the backend for \textbf{ authentication, Databases}, and Cart
      Products.
      \item  Stripe \textbf{Payment gateway} is used for \textbf{online payment} which
      \textbf{improves} business \textbf{sales} by about \textbf{200\%.}
    \end{tightemize}


    \section*{Achievements} 
    \begin{tabular}{rll}
    2022	  &  \textbf{1\textsuperscript{st} Prize} & \href{https://drive.google.com/drive/folders/13uV6u1qge0kMAJ67J84DtnbJjgjbHjSGtBizGmAzotTOa0BFClvEWlYaDQQeQMJbOVtBXxCk}{Idea Pitching \textbf{Startup Cell NIT AP}} \\
    2022	     & \textbf{ 41/15000}  & \href{https://drive.google.com/file/d/1atilxo1LnxKXvUW8hDytg__F1Dpe0FDC/view}{\textbf{CodeChef Long Dec Challenge}}\\
    2022  & \textbf{3452 \textsuperscript{th}} & \href{https://drive.google.com/file/d/1BiwyVlzI5dh4EW5C9SVCS4j_vrKi3bdd/view}{\textbf{Google KickStart Round H}}\\
    2022	     &  \textbf{1\textsuperscript{st} Prize} & \href{https://drive.google.com/file/d/11MtJKzNPpVAdR6VWHuizrE2ros0bHbOS/view}{ \textbf{Designathon Hakathon} NIT AP} \\
    2022 & \textbf{ 250\textsuperscript{+}} & Questions solved on \href{https://auth.geeksforgeeks.org/user/rahulsah6003/practice/}{\textbf{LeetCode}} \& \href{https://leetcode.com/rahulsah6003/}{\textbf{GFG}}
    \end{tabular}


  \end{flushleft}



\end{multicols}

\end{document}